Hydrodynamics of a Semi-Permeable Vesicle Under Flow and Confinement???

### 2020-12-17 vesicle_code/docs/permeableVes/main.tex
working on contracting

\begin{figure*}[htp]
  \ifTikz
  \input{figures/stenosisComposite.tikz}
  \fi
  \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
  passing through a constricted geometry similar to the experimental
  device in~\cite{abk-fai-sto2006}. (b) A semi-permeable vesicle passing
  through a constricted geometry that is over five times longer. (c) The
  excess pressure of an impermeable and semi-permeable vesicle in the
  short geometry in (a). (d) The reduced area of the semi-permeable
  vesicle in the short geometry in (a). (e) The reduced area of the
  semi-permeable vesicle in the long geometry in (b). In parts (c), (d),
  and (e), the horizontal axis is the x-coordinate of the vesicle's
  center of mass.}
\end{figure*}

@@

In Figures~\ref{fig:contractingComposite}(a)
and~\ref{fig:contractingComposite}(b), we plot snapshots of vesicles
with different permeability rates, and
Figure~\ref{fig:contractingComposite}(c) shows that the reduced area as
a function of the vesicles' location. For sufficiently large
permeability rates, the vesicle initially inflates, but then deflates as
it passes through the constriction. However, if the semi-permeability
rate is too low, the vesicle is too large when it reaches the narrowest
part of the channel, and it is unable to pass. In
Figures~\ref{fig:contractingComposite}(d)
and~\ref{fig:constractingComposite}{e}, we plot snapshots of vesicles
with different imposed maximum velocities, and
Figure~\ref{fig:contractingComposite}(f) shows that the reduced area as
a function of the vesicles' location. At low velocities, the vesicle
inflates similar to the unbounded parabolic flow example, and it is
unable to pass through the constrictions. However, higher flow rates
result in additional deflation and the vesicle passes through the
contraction.

To understand long term effects of a vesicle passing through a
contracting geometry, in Figures~\ref{fig:contractingComposite}(g) we
simulate a vesicle passing six times through the contracting geometry.
In Figure~\ref{fig:contractingComposite}(h), we show that the vesicle
deflates each time it passes through the constriction followed by a
rapid inflation. The total area loss over the history of the vesicle is
almost 50\%. In Figure~\ref{fig:contractingComposite}(i), we show the
vesicle velocity as a function of the vesicle's center of mass. As the
vesicle passes through the contraction, it accelerates followed by a
rapid deacceleration once it has passed through the contraction.

>>>>

\begin{figure*}[htp]
%  \ifTikz
  \input{figures/stenosisComposite.tikz}
%  \fi
  \caption{\label{fig:stenosisComposite} (a) A semi-permeable vesicle
  passing through a constricted geometry similar to the experimental
  device in~\cite{abk-fai-sto2006}. (b) A semi-permeable vesicle passing
  through a constricted geometry that is over five times longer. (c) The
  excess pressure of an impermeable and semi-permeable vesicle in the
  short geometry in (a). (d) The reduced area of the semi-permeable
  vesicle in the short geometry in (a). (e) The reduced area of the
  semi-permeable vesicle in the long geometry in (b). In parts (c), (d),
  and (e), the horizontal axis is the x-coordinate of the vesicle's
  center of mass.}
\end{figure*}

@@

In Figures~\ref{fig:contractingComposite}a
and~\ref{fig:contractingComposite}b, we plot snapshots of vesicles with
different permeability rates, and Figure~\ref{fig:contractingComposite}c
shows that the reduced area as a function of the vesicles' location. For
sufficiently large permeability rates, the vesicle initially inflates,
but then deflates as it passes through the constriction. However, if the
semi-permeability rate is too low, the vesicle is too large when it
reaches the narrowest part of the channel, and it is unable to pass. In
Figures~\ref{fig:contractingComposite}d
and~\ref{fig:contractingComposite}e, we plot snapshots of vesicles with
different imposed maximum velocities, and
Figure~\ref{fig:contractingComposite}f shows that the reduced area as a
function of the vesicles' location. At low velocities, the vesicle
inflates similar to the unbounded parabolic flow example, and it is
unable to pass through the constrictions. However, higher flow rates
result in additional deflation and the vesicle passes through the
contraction.

To understand long term effects of a vesicle passing through a
contracting geometry, in Figures~\ref{fig:contractingComposite}g we
simulate a vesicle passing six times through the contracting geometry.
In Figure~\ref{fig:contractingComposite}h, we show that the vesicle
deflates each time it passes through the constriction followed by a
rapid inflation. The total area loss over the history of the vesicle is
almost 50\%. In Figure~\ref{fig:contractingComposite}i, we show the
vesicle velocity as a function of the vesicle's center of mass. As the
vesicle passes through the contraction, it accelerates followed by a
rapid deacceleration once it has passed through the contraction.
